Leaf traits drive differences in biomass partitioning among major plant functional types

### 2015-08-11 manuscript.Rnw
Moved sample size tables to one combined table in main manuscript.

>>>>

<<results='asis'>>=
bigtable <- rbind(cbind(c("LMF","","",""),c("DA","EA","EG","Sum"), table_lmf),
                  cbind(c("LAR","","",""),c("DA","EA","EG","Sum"), table_lar), 
                  cbind(c("MF/AS","","",""),c("DA","EA","EG","Sum"), table_mlfastba),
                  cbind(c("AF/AS","","",""),c("DA","EA","EG","Sum"), table_alfastba))
rownames(bigtable) <- NULL
colnames(bigtable)[1:2] <- c("Variable","PFT")

print(xtable(bigtable, align="llrlll|l",
               caption="Sample sizes used in the analyses of the four variables considered in the study (LMF, LAR, MF/AS and AF/AS), by plant functional type (PFT) and biome.  Sample sizes denote number of individuals, with number of unique species in parentheses. ",
             label="table:counttable"
               ), hline.after=c(0,4,8,12,16), caption.placement="top",
      include.rownames=FALSE)
@
